### 2013-11-06 code/multilevel_models.Rmd
All ready for Turku seminar. Now back in using the latest version of texreg 1.30.1. Thanks Philip!

@@

summary(bisoc.1 <- lmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.2 <- lmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.3 <- lmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.4 <- lmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.5 <- lmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.6 <- lmer(pov.log.social ~ crise+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.7 <- lmer(pov.log.social ~ group1+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.8 <- lmer(pov.log.social ~ uw.gini+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.9 <- lmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                        family = binomial, data=df))
summary(bisoc.10 <- lmer(pov.log.social ~ wbgi.vae+(1|cntry),
                         family = binomial, data=df))

summary(biind.1 <- lmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial, data=df))
summary(biind.2 <- lmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial, data=df))
summary(biind.3 <- lmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial, data=df))
summary(biind.4 <- lmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial, data=df))
summary(biind.5 <- lmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial, data=df))
summary(biind.6 <- lmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial, data=df))
summary(biind.7 <- lmer(pov.log.individual ~ group1+(1|cntry),
                        family = binomial, data=df))
summary(biind.8 <- lmer(pov.log.individual ~ uw.gini+(1|cntry),
                        family = binomial, data=df))
summary(biind.9 <- lmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial, data=df))
summary(biind.10 <- lmer(pov.log.individual ~ wbgi.vae+(1|cntry),
                         family = binomial, data=df))

summary(soc.0 <- lmer(pov.log.social ~ (1|cntry),
                      family = binomial, data=df))
summary(soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial, data=df))
summary(soc.2 <- lmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+(1|cntry),family = binomial, data=df))
summary(soc.3 <- lmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+gdpchange07.10+(1|cntry),family = binomial, data=df))
summary(soc.4 <- lmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+gdpchange07.10+wbgi.vae+(1|cntry),family = binomial, data=df))

summary(ind.0 <- lmer(pov.log.individual ~ (1|cntry),
                      family = binomial, data=df))
summary(ind.1 <- lmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial, data=df))
summary(ind.2 <- lmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+(1|cntry),family = binomial, data=df))
summary(ind.3 <- lmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+gdpchange07.10+(1|cntry),family = binomial, data=df))
summary(ind.4 <- lmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw.gini+gdpchange07.10+wbgi.vae+(1|cntry),family = binomial, data=df))
```

>>>>

% Multilevel modelling

@@

summary(biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.7 <- glmer(pov.log.individual ~ group1+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.8 <- glmer(pov.log.individual ~ uw.gini+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.9 <- glmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data=df))
summary(biind.10 <- glmer(pov.log.individual ~ wbgi.vae+(1|cntry),
                         family = binomial(logit), data=df))

summary(soc.0 <- glmer(pov.log.social ~ (1|cntry),
                      family = binomial(logit)(logit),
                       data=df.multi))
summary(soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                         past.diff+future.diff+crise+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(soc.2 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(soc.3 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))

summary(ind.0 <- glmer(pov.log.individual ~ (1|cntry),
                      family = binomial(logit),
                       data=df.multi))
summary(ind.1 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                       data=df.multi))
summary(ind.2 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(ind.3 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
summary(ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data=df.multi))
```

### 2013-11-06 index.Rmd
All ready for Turku seminar. Now back in using the latest version of texreg 1.30.1. Thanks Philip!

cd ~/workspace/lits/attrib/attrib_year2013/figure
lftp -u np16003 -e "mirror -R;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/figure
```

@@

date      comment
--------  -------------------
20131103  Regression modelling in process. Final models will be published on Tuesday afternoon

@@

- [Final tables as A4 .pdf](finalTables.pdf)

@@

- HSE Moscow - November 12, 2013
- Jatkokoulutusseminaari Turku November 7, 2013
- [ESA Torino - August 29, 2013](torino2013/TorinoSlides2013_final.html)

>>>>

cd ~/workspace/lits/attrib/attrib_year2013/figure
lftp -u np16003 -e "mirror -R;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/figure

cd ~/workspace/lits/attrib/attrib_year2013/turku2013
lftp -u np16003 -e "mput *.html;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/turku2013
```

@@

date      comment
--------  -------------------
20131103  Regression modelling in process. Final models will be published on Tuesday afternoon
20131105  Regression modelling almost finished. Bug in a software caused a delay. Will be fixed by Wed morning. Now the tables are there, but coef and model names are not customized.
20131106  Regression modelling somewhat done for Turku seminar.

@@

@@

- HSE Moscow - November 12, 2013
- [Jatkokoulutusseminaari Turku November 7, 2013](turku2013/slidesTkuJatko20131107.html)
- [ESA Torino - August 29, 2013](torino2013/TorinoSlides2013_final.html)

### 2013-11-06 regressionModelling.Rmd
All ready for Turku seminar. Now back in using the latest version of texreg 1.30.1. Thanks Philip!

```{rmultilevelLoadData}
library(lme4)
#########################################
#########################################
setwd("~/workspace/lits/attrib/attrib_year2013/")

@@

date      comment
--------  -------------------
20131103  Non multi-level logistic regression done but not interpret yet. Bivariate multilevel models the same. Multivariate multilevel models running over night.

@@

#### Diagnostics of the final model

```{r}
confint(mulbisoc.6)
```

```{r}
exp(cbind(OR = coef(mulbisoc.6), confint(mulbisoc.6)))
```

```{r}
newdata2 <- with(df.model, data.frame(gre = rep(seq(from = 200, to = 800, length.out = 100),
    4), gpa = mean(gpa), rank = factor(rep(1:4, each = 100))))

newdata3 <- cbind(newdata2, predict(mylogit, newdata = newdata2, type = "link",
    se = TRUE))
newdata3 <- within(newdata3, {
    PredictedProb <- plogis(fit)
    LL <- plogis(fit - (1.96 * se.fit))
    UL <- plogis(fit + (1.96 * se.fit))
})

ggplot(newdata3, aes(x = gre, y = PredictedProb)) + geom_ribbon(aes(ymin = LL,
    ymax = UL, fill = rank), alpha = 0.2) + geom_line(aes(colour = rank),
    size = 1)

@@

```{rmultiNomSimple}

@@

```{rmultiNomSimpleOutput, results='asis'}

@@

## Multivariate multinomial logistic regression

@@

```{rmultilevelBivarSoc}
bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
 bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
#  bisoc.7 <- glmer(pov.log.social ~ group_general+(1|cntry),
#                          family = binomial(logit), data = df.model)
 bisoc.8 <- glmer(pov.log.social ~ uw_gini+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.9 <- glmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)

```{rregressionBivarSocOutput, results='asis'}

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      #"Country grouping (CIS vs. CEE)",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          #bisoc.7,
          bisoc.8,
          bisoc.9,bisoc.10),
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
# biind.7 <- glmer(pov.log.individual ~ group_general+(1|cntry),
#                         family = binomial(logit), data = df.model)
biind.8 <- glmer(pov.log.individual ~ uw_gini+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
```

```{rmultilevelBivarIndOuput, results='asis'}
library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          #biind.7,
          biind.8,
          biind.9,biind.10),
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)
```

@@

```{rmultilevelMultiSoc}
library(lme4)
soc.0 <- glmer(pov.log.social ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                      data = df.model)
soc.2 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.3 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiSocOutput, results='asis'}
model.names.multi = c("Empty",
                      "Only individual",
                      "Gini added",
                      "GDP change added",
                      "Good governance added")

htmlreg(list(soc.0,
        soc.1,
        soc.2,
        soc.3,
        soc.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
          caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)
```

@@

```{rmultilevelMultiInd, eval=FALSE}
ind.0 <- glmer(pov.log.individual ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.1 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.2 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.3 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
```

```{rmultilevelMultiIndOutput, results='asis', eval=FALSE}
htmlreg(list(soc.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
          caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)
```

>>>>

```{rmultilevelLoadData}
#########################################
#########################################
setwd("~/workspace/lits/attrib/attrib_year2013/")

@@

date      comment
--------  -------------------
20131103  Non multi-level logistic regression done but not interpret yet. Bivariate multilevel models the same. Multivariate multilevel models running over night.
20131105  Regression modelling almost finished. Bug in a software caused a delay. Will be fixed by Wed morning. Now the tables are there, but coef and model names are not customized.
20131106  Model names fixed. Multinomial models coming by midday

@@

@@

<!--

### using nnet-package

This model follows tutorial by UCLA [Multinomial regression](http://www.ats.ucla.edu/stat/r/dae/mlogit.htm) and it uses [nnet](http://cran.r-project.org/web/packages/nnet/index.html)-package.

-->

```{rmultiNomSimplennet, eval=FALSE, echo=FALSE}
library(nnet)
df.model$poverty2 <- relevel(df.model$poverty, ref = "Social Blame")
test <- multinom(poverty2 ~ incsour3 + edu2 + income2 +
                   past.diff + future.diff + crise, data = df.model)
#library(texreg)
#screenreg(list(test))
summary(test)$coefficients/summary(test)$standard.errors

# The ratio of the probability of choosing one outcome category over the
# probability of choosing the baseline category is often referred as relative
# risk (and it is also sometimes referred as odds as we have just used to
# described the regression parameters above). The relative risk is the right-hand
# side linear equation exponentiated, leading to the fact that the exponentiated
# regression coefficients are relative risk ratios for a unit change in the
# predictor variable. We can exponentiate the coefficients from our model to see
# these risk ratios.

exp(coef(test))

@@

### using mlogit-package

This follows the example from [University of Toronto](http://www.utstat.toronto.edu/~brunner/oldclass/312f12/lectures/MultinomialLogitWithR.pdf) and [Discrete-Choice Logit Models with R by Philip A. Viton (October 26, 2013)](http://facweb.knowlton.ohio-state.edu/pviton/courses2/crp5700/5700-mlogit.pdf)

```{rmultiNomSimpleMlogit, results='markup'}
library(mlogit)
dat.mlogit <- df.model[,c("poverty","edu2","incsour3","income2",
                          "past.diff","future.diff","crise")]
 dat.mlogit <- mlogit.data(dat.mlogit, shape="wide", choice="poverty")
# 
# 
# model.mlogit1 <- mlogit(poverty ~ 0 | incsour3,
#                                data = dat.mlogit, 
#                                reflevel ="Social Blame")
# model.mlogit2 <- mlogit(poverty ~ 0 | incsour3 + edu2,
#                                data = dat.mlogit, 
#                                reflevel ="Social Blame")
# model.mlogit3 <- mlogit(poverty ~ 0 | incsour3 + edu2 + 
#                                       past.diff,
#                                data = dat.mlogit, 
#                                reflevel ="Social Blame")
# model.mlogit4 <- mlogit(poverty ~ 0 | incsour3 + edu2 + 
#                                       past.diff + future.diff,
#                                data = dat.mlogit, 
#                                reflevel ="Social Blame")
model.mlogit5 <- mlogit(poverty ~ 0 | incsour3 + edu2 + 
                                      past.diff + future.diff +
                                      crise, 
                               data = dat.mlogit, 
                               reflevel ="Social Blame")

summary(model.mlogit5)
```

```{r, eval=FALSE, echo=FALSE}

screenreg(list(model.mlogit1,model.mlogit2))

f <- coeftest(model.mlogit)
xtable(as.data.frame(f))model1 <- multinom(formula = reason ~ supu+income, data = ml.06)

summary(m)
coeftest(m)

X <- mlogit.data(ml.10, shape="wide", choice="poverty")
coeftest(mlogit(poverty ~ 0 | success,
               data = X, reflevel ="Because of injustice in our society"))
summary(mlogit(poverty ~ 0 | success,
                data = X, reflevel ="Because of injustice in our society"))

coef(mlogit(poverty ~ 0 | success,
               data = X, reflevel ="Because of injustice in our society"))

@@

## Multilevel multinomial logistic regression

Can be modelled in R in Bayesian manner using either [ChoiceModelR](http://cran.r-project.org/web/packages/ChoiceModelR/index.html) and  [Zelig](http://cran.r-project.org/web/packages/Zelig/).

Marco Steenbergen discusses the stat theory and imlementation in Stata in this video

<iframe width="420" height="315" src="//www.youtube.com/embed/q_t9VerQ2ko" frameborder="0" allowfullscreen></iframe>

@@

```{rmultilevelBivarSoc}
library(lme4)
bisoc.1 <- glmer(pov.log.social ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.2 <- glmer(pov.log.social ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.3 <- glmer(pov.log.social ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.4 <- glmer(pov.log.social ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
bisoc.5 <- glmer(pov.log.social ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
 bisoc.6 <- glmer(pov.log.social ~ crise+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.8 <- glmer(pov.log.social ~ uw_gini+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.9 <- glmer(pov.log.social ~ gdpchange07.10+(1|cntry),
                         family = binomial(logit), data = df.model)
 bisoc.10 <- glmer(pov.log.social ~ wbgi_vae+(1|cntry),
                          family = binomial(logit), data = df.model)
```

```{rmultilevelBivarSocOutputNOCI, results='asis'}

coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

library(texreg)
htmlreg(list(bisoc.1,bisoc.2,
          bisoc.3,bisoc.4,
          bisoc.5,bisoc.6,
          bisoc.8,
          bisoc.9,bisoc.10),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Bivariate social blame", caption.above=TRUE)

@@

```{rmultilevelBivarInd}
biind.1 <- glmer(pov.log.individual ~ incsour3+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.2 <- glmer(pov.log.individual ~ edu2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.3 <- glmer(pov.log.individual ~ income2+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.4 <- glmer(pov.log.individual ~ past.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.5 <- glmer(pov.log.individual ~ future.diff+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.6 <- glmer(pov.log.individual ~ crise+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.8 <- glmer(pov.log.individual ~ uw_gini+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.9 <- glmer(pov.log.individual ~ gdpchange07.10+(1|cntry),
                        family = binomial(logit), data = df.model)
biind.10 <- glmer(pov.log.individual ~ wbgi_vae+(1|cntry),
                         family = binomial(logit), data = df.model)
```

```{rmultilevelBivarIndOuputNOCI, results='asis'}
library(texreg)
htmlreg(list(biind.1,biind.2,
          biind.3,biind.4,
          biind.5,biind.6,
          biind.8,
          biind.9,biind.10),
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        use.packages=FALSE,
        include.pvalues=TRUE,
        caption="Bivariate individual blame", 
        caption.above=TRUE)
```

@@

```{rmultilevelMultiSoc}
library(lme4)

soc.0 <- glmer(pov.log.social ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
soc.1 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                      data = df.model)
soc.2 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.3 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

@@

```{rmultilevelMultiSocOutputNOCI, results='asis'}
coef.names.multi = c("(intercept)", 
                      "Dependent","Low education",
                      "Low income","Income has worsened",
                      "Income will worsen","Has affected great or fair amount",
                      "Gini coefficient",
                      "Change in GDP between 2007 to 2010",
                      "Good governance")

model.names.multi = c("Empty",
                      "Only individual",
                      "Gini added",
                      "GDP change added",
                      "Good governance added")

htmlreg(list(soc.0,
        soc.1,
        soc.2,
        soc.3,
        soc.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

@@

```{rmultilevelMultiInd}

ind.0 <- glmer(pov.log.individual ~ (1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.1 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+(1|cntry),
                      family = binomial(logit),
                       data = df.model)
ind.2 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.3 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+(1|cntry),
                       family = binomial(logit),
                       data = df.model)
ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

```{rmultilevelMultiIndOutputNOCI, results='asis'}

htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
          caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

### Comparison of full models with our last model

```{rmultilevelMultivarFull}

soc.4 <- glmer(pov.log.social ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

ind.4 <- glmer(pov.log.individual ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

df.model$pov.log.socVsInc[df.model$poverty == "Social Blame"] <- 1
df.model$pov.log.socVsInc[df.model$poverty == "Individual Blame"] <- 0

socVsInc <- glmer(pov.log.socVsInc ~ incsour3+edu2+income2+
                        past.diff+future.diff+crise+
                        uw_gini+gdpchange07.10+wbgi_vae+(1|cntry),
                       family = binomial(logit),
                       data = df.model)

```{rrmultilevelMultivarFullOutput, results='asis', eval=TRUE}
model.names.multi.2 = c("Social blame vs. not",
                      "Individual blame vs. not",
                        "Social blame vs. Individual blame")

library(texreg)
htmlreg(list(soc.4,ind.4,socVsInc),
        naive = TRUE,
        custom.model.names = model.names.multi.2,
        custom.coef.names = coef.names.multi,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social and individual blame type of explanation", 
        caption.above=TRUE)
